---
title: "P8105 Homework 6"
name: "Jessie Wong"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(modelr)
library(mgcv)
```

**Context**: This assignment reinforces ideas in Linear Models.

## Problem 1 
Create a `city_state` variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. Modifiy victim_race to have categories  white and non-white, with white as the reference category. Be sure that victim_age is numeric

```{r}
# Loaded the dataset, created a binary variable, omitted the specific cities, and modified `victim_race` to be categorical
homicide = read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv", na = c("", "NA", "Unknown")) %>%
  mutate(
    city_state = str_c(city, state, sep = ", "),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved"
    )
  ) %>% 
  filter(city_state != "Tulsa, AL", city_state != "Dallas, TX", city_state != "Phoenix, AZ", city_state != "Kansas City, MO") %>%
  mutate(victim_race = ifelse(victim_race != "White", "Non-White", "White"), 
         victim_race = fct_relevel(victim_race, "White"))
  
# Checked to see if `victim_age` is numeric
is.numeric(homicide$victim_age)
# Confirmed that victim_age is numeric 
```

For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race (as just defined) as predictors. Save the output of glm as an R object; apply the broom::tidy to this object; and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing non-white victims to white victims keeping all other variables fixed.
```{r}
baltimore = homicide %>%
  filter(city_state == "Baltimore, MD") %>%
  mutate(solved = as.numeric(resolution == "solved")) %>%
  select(solved, victim_age, victim_race, victim_sex) %>%
  glm(solved ~ victim_age + victim_race + victim_sex, data = ., family = binomial())
  
baltimore %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate),
         CI_low = exp(estimate - (1.96 * std.error)),
         CI_high = exp(estimate + (1.96 * std.error))) %>%
  select(term, OR, p.value, CI_low, CI_high) %>% 
  knitr::kable(digits = 3) 
```
The odds of a homicide being solved for `Non-white` victims is 0.441 times the odds of a homicide being solved for `White` victims. There is a 95% confidence that the true odds ratio lies between 0.313 and 0.620. 

Now run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing non-white victims to white victims. Do this within a “tidy” pipeline, making use of  purrr::map, list columns, and unnest as necessary to create a dataframe with estimated ORs and CIs for each city.
```{r}
allcities = homicide %>%
  mutate(solved = as.numeric(resolution == "solved")) %>%
  group_by(city_state) %>%
  nest() %>%
  mutate(allglms = map(data, ~glm(solved ~ victim_age + victim_race + victim_sex, data = ., family = binomial())),
             allresult = map(allglms, broom::tidy)) %>%
  select(-data, -allglms) %>%
  unnest() %>%
  filter(term == "victim_raceNon-White") %>%
  mutate(OR = exp(estimate), 
         CI_low = exp(estimate - (1.96 * std.error)),
         CI_high = exp(estimate + (1.96 * std.error))) %>%
  select(city_state, OR, CI_low, CI_high)
```

Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.
```{r}
allcities %>%
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() +
  geom_errorbar(aes(ymin = CI_low, ymax = CI_high)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(
    title = "Odds ratio of Solved Homicides Among White Vs. Non-White Victims Across U.S. Cities",
    x = "City, State",
    y = "Odds Ratio")
```
From the plot above, across almost all the cities in our analysis the odds of a homicide being solved for `non-white` victims is lower than for `white` victims, with the except of Birmingham, Al, Durham, NC (on the null), and Tampa, Fl. We see a particularly large difference in the odds of solved homicides between non-white and white victim in Bostom, MA, Omaha, NE, and Oakland, CA.  

## Problem 2
In this problem, I will analyze data gathered to understand the effects of several variables on a child’s birthweight. This dataset, consists of roughly 4000 children and includes the variables specified in the homework instructions.

Load and clean the data for regression analysis (i.e. convert numeric to factor where appropriate, check for missing data, etc.).
```{r}
children = read_csv("data/birthweight.csv") %>% 
  mutate(babysex = as.factor(babysex),
         frace = as.factor(frace), 
         malform = as.factor(malform),
         mrace = as.factor(mrace),
         babysex = recode(babysex, "1" = "Male", "2" = "Female"),
         malform = recode(malform, "1" = "Present", "0" = "Absent"),
         frace = recode(frace, "1" = "White", "2" = "Black", "3" = "Asian", "4" = "Puerto Rican", "8" = "Other", "9" = "Unknown"),
         mrace = recode(mrace, "1" = "White", "2" = "Black", "3" = "Asian", "4" = "Puerto Rican", "8" = "Other"))

# Check to identify any NAs in the dataset
sum(is.na(children))
                                      
View(children)
```

Propose a regression model for birthweight. This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.
```{r}
# Model Fitting
mod1 = children %>%
  lm(bwt ~ fincome + momage + blength, data = .)

# Tidying Output
mod1  %>%
  broom::glance()
mod1 %>%
  broom::tidy() %>%
  select(term, estimate, p.value) %>%
  knitr::kable(digit = 3)

# Diagnostics

children %>% 
  modelr::add_residuals(mod1) %>%
  modelr::add_predictions(mod1) %>%
  ggplot(aes(x = resid, y = pred)) + 
  geom_point() + 
  labs(
    title = "Model residuals Against Fitted Values For Birthweights",
    x = "Residuals",
    y = "Predictions")
```

Compare your model to two others:

One using length at birth and gestational age as predictors (main effects only)
One using head circumference, length, sex, and all interactions (including the three-way interaction) between these

Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate.

Note that although we expect your model to be reasonable, model building itself is not a main idea of the course and we don’t necessarily expect your model to be “optimal”.
```{r}
cv = crossv_mc(children, 100)

cv %>% pull(train) %>% .[[1]] %>% as_tibble
cv %>% pull(test) %>% .[[1]] %>% as_tibble

mod1 = lm(bwt ~ fincome + momage + blength, data = children)
mod2 = lm(bwt ~ blength + gaweeks, data = children)
mod3 = lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = children)

children %>% 
  gather_predictions(mod1, mod2, mod3) %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = blength, y = bwt)) + 
  geom_point(alpha = .5) +
  geom_line(aes(y = pred), color = "red") + 
  facet_grid(~model)

cv = cv %>% 
  mutate(mod1 = map(train, ~lm(bwt ~ fincome + momage + blength, data = .x)),
         mod2 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
         mod3 = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = .x)),
         rmse_mod1 = map2_dbl(mod1, test, ~rmse(model = .x, data = .y)),
         rmse_mod2 = map2_dbl(mod2, test, ~rmse(model = .x, data = .y)),
         rmse_mod3 = map2_dbl(mod3, test, ~rmse(model = .x, data = .y)))

cv %>% 
  select(starts_with("rmse")) %>% 
  gather(key = model, value = rmse) %>% 
  mutate(model = str_replace(model, "rmse_", ""),
         model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```



